\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}
\setlength{\tabcolsep}{0in}
\raggedbottom
\raggedright

\titleformat{\section}
  {\vspace{-2pt}\color{black}\rule{\linewidth}{0.5pt}\vspace{2pt}\\\scshape\large\raggedright}
  {}{0em}{}

\titlespacing{\section}{0pt}{6pt}{2pt}
\setlist[itemize]{leftmargin=0.15in, itemsep=2pt, topsep=2pt}
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  {\Huge \scshape Max Heitzman} \\ \vspace{1pt}
  \small Lubbock, TX $|$ (214) 543-2528 $|$ \href{mailto:maxheitzman@gmail.com}{maxheitzman@gmail.com} $|$ \href{https://github.com/maxheitzman}{github.com/maxheitzman} $|$ \href{https://linkedin.com/in/maxheitzman}{linkedin.com/in/maxheitzman} \\
  \vspace{2pt}
  \textit{Aspiring AI-focused graduate student with a background in systems programming, algorithms, and applied computing.}
\end{center}

\vspace{-6pt}
\section*{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Texas Tech University}{Expected: Dec 2025}
  {B.S. Computer Science, Minor in Mathematics}{Lubbock, TX}
  \resumeItemListStart
    \resumeItem{GPA (Last 60 hrs): $\sim$3.4}
    \resumeItem{Relevant Coursework: Data Structures, Algorithms, OOP, Programming Languages, ISA, Math Statistics}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-6pt}
\section*{Projects}
\resumeSubHeadingListStart
\resumeSubheading
  {Multiprocessor Cellular Automaton Simulator}{Apr 2025}
  {Python — Parallel Programming}{GitHub}
  \resumeItemListStart
    \resumeItem{Two-phase simulator evolves matrix state via symbolic rules.}
    \resumeItem{Implemented multiprocessing for 40\% runtime gain over serial.}
  \resumeItemListEnd

\resumeSubheading
  {Syntax Parser}{Mar 2025}
  {C — Compiler Design}{GitHub}
  \resumeItemListStart
    \resumeItem{Recursive descent parser validates grammar using BNF rules.}
    \resumeItem{Consumes token stream output from lexical analyzer.}
  \resumeItemListEnd

\resumeSubheading
  {Lexical Analyzer}{Feb 2025}
  {C — Language Processing}{GitHub}
  \resumeItemListStart
    \resumeItem{Classifies lexemes as keywords, identifiers, literals, or operators.}
    \resumeItem{Handles syntax edge cases in symbolic streams.}
  \resumeItemListEnd

\resumeSubheading
  {QuickHybridSort Analysis}{Spring 2025}
  {Python — Algorithms}{GitHub}
  \resumeItemListStart
    \resumeItem{Benchmarked QuickSort/InsertionSort hybrid across input sizes.}
    \resumeItem{Plotted crossover point to determine optimal threshold.}
  \resumeItemListEnd

\resumeSubheading
  {0/1 Knapsack Zoo Trip Simulator}{Spring 2025}
  {Python — Dynamic Programming}{GitHub}
  \resumeItemListStart
    \resumeItem{Applied bottom-up DP to plan optimal zoo routes under constraints.}
  \resumeItemListEnd

\resumeSubheading
  {OOP Java Tools}{Spring 2025}
  {Java — Serialization, I/O, Exceptions}{Texas Tech}
  \resumeItemListStart
    \resumeItem{Built file tools, test scorer, and calculator using Java OOP.}
  \resumeItemListEnd

\resumeSubheading
  {Assembly Language Programming}{Fall 2024}
  {x86 Assembly — Computer Org.}{Texas Tech}
  \resumeItemListStart
    \resumeItem{Wrote MASM programs for Fibonacci, RNGs, and endian conversion.}
    \resumeItem{Demonstrated register usage, memory control, and array indexing.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-6pt}
\section*{Technical Skills}
\begin{itemize}
  \item[]
  \small{
  \textbf{Programming Languages:} \\
  \hspace{1em} \textbf{Proficient:} C, Python, Java \\
  \hspace{1em} \textbf{Familiar:} x86 Assembly, Bash, LaTeX, C++, Scheme, Prolog \\
  \hspace{1em} \textbf{Learning:} JavaScript, SQL

  \vspace{4pt}
  \textbf{Tools:} Git, VS Code, Overleaf, MobaXterm, Eclipse, PyCharm, Linux (HPCC), CLI Editing \\
  \textbf{Concepts:} Lexical Analysis, Parsing, Recursion, OOP, Multiprocessing, Dynamic Programming, ISA
  }
\end{itemize}

\vspace{-6pt}
\section*{Organizations}
\resumeSubHeadingListStart
\resumeSubheading
  {Google Developer Student Club (GDSC)}{Aug 2023 – Present}
  {Member, Texas Tech University}{}
\resumeSubheading
  {Association for Computing Machinery (ACM)}{Aug 2023 – Present}
  {Member, Texas Tech University}{}
\resumeSubHeadingListEnd

\end{document}
